Total Platform Cyber Protection

### 2016-08-21 paper.tex
added hardware and firmware sections, made biblio work

% Head 1
\section{MMSN Protocol}

% Head 2
\subsection{Frequency Assignment}

We propose a suboptimal distribution to be used by each node, which is
easy to compute and does not depend on the number of competing
nodes. A natural candidate is an increasing geometric sequence, in
which
% Numbered Equation
\begin{equation}
\label{eqn:01}
P(t)=\frac{b^{\frac{t+1}{T+1}}-b^{\frac{t}{T+1}}}{b-1},
\end{equation}
where $t=0,{\ldots}\,,T$, and $b$ is a number greater than $1$.

In our algorithm, we use the suboptimal approach for simplicity and
generality. We need to make the distribution of the selected back-off
time slice at each node conform to what is shown in Equation
(\ref{eqn:01}). It is implemented as follows: First, a random
variable $\alpha$ with a uniform distribution within the interval
$(0, 1)$ is generated on each node, then time slice $i$ is selected
according to the following equation:
% Unnumbered Equation
\[
i=\lfloor(T+1)\log_b[\alpha(b-1)+1]\rfloor.
\]
It can be easily proven that the distribution of $i$ conforms to Equation
(\ref{eqn:01}).

So protocols [Bahl 2002,Culler 2001,Zhou 2006,Adya 2001,Culler 2001;
Tzamaloukas-01; Akyildiz-01] that use RTS/CTS
controls\footnote{RTS/CTS controls are required to be implemented by
802.11-compliant devices. They can be used as an optional mechanism
to avoid Hidden Terminal Problems in the 802.11 standard and
protocols based on those similar to [Akyildiz 2001] and
[Adya 2001].} for frequency negotiation and reservation are not
suitable for WSN applications, even though they exhibit good
performance in general wireless ad hoc
networks.

% Head 3
\subsubsection{Exclusive Frequency Assignment}

In exclusive frequency assignment, nodes first exchange their IDs
among two communication hops so that each node knows its two-hop
neighbors' IDs. In the second broadcast, each node beacons all
neighbors' IDs it has collected during the first broadcast period.

% Head 4
\paragraph{Eavesdropping}

Even though the even selection scheme leads to even sharing of
available frequencies among any two-hop neighborhood, it involves a
number of two-hop broadcasts. To reduce the communication cost, we
propose a lightweight eavesdropping scheme.

\subsection{Basic Notations}

As Algorithm~\ref{alg:one} states, for each frequency
number, each node calculates a random number (${\textit{Rnd}}_{\alpha}$) for
itself and a random number (${\textit{Rnd}}_{\beta}$) for each of its two-hop
neighbors with the same pseudorandom number generator.
% Algorithm
\begin{algorithm}[t]
\SetAlgoNoLine
\KwIn{Node $\alpha$'s ID ($ID_{\alpha}$), and node $\alpha$'s
neighbors' IDs within two communication hops.}
\KwOut{The frequency number ($FreNum_{\alpha}$) node $\alpha$ gets assigned.}
$index$ = 0; $FreNum_{\alpha}$ = -1\;
\Repeat{$FreNum_{\alpha} > -1$}{
        $Rnd_{\alpha}$ = Random($ID_{\alpha}$, $index$)\;
        $Found$ = $TRUE$\;
        \For{each node $\beta$ in $\alpha$'s two communication hops
    }{
      $Rnd_{\beta}$ = Random($ID_{\beta}$, $index$)\;
      \If{($Rnd_{\alpha} < Rnd_{\beta}$) \text{or} ($Rnd_{\alpha}$ ==
          $Rnd_{\beta}$ \text{and} $ID_{\alpha} < ID_{\beta}$)\;
      }{
        $Found$ = $FALSE$; break\;
      }
        }
     \eIf{$Found$}{
           $FreNum_{\alpha}$ = $index$\;
         }{
           $index$ ++\;
     }
      }
\caption{Frequency Number Computation}
\label{alg:one}
\end{algorithm}

Bus masters are divided into two disjoint sets, $\mathcal{M}_{RT}$
and $\mathcal{M}_{NRT}$.
% description
\begin{description}
\item[RT Masters]
$\mathcal{M}_{RT}=\{ \vec{m}_{1},\dots,\vec{m}_{n}\}$ denotes the
$n$ RT masters issuing real-time constrained requests. To model the
current request issued by an $\vec{m}_{i}$ in $\mathcal{M}_{RT}$,
three parameters---the recurrence time $(r_i)$, the service cycle
$(c_i)$, and the relative deadline $(d_i)$---are used, with their
relationships.
\item[NRT Masters]
$\mathcal{M}_{NRT}=\{ \vec{m}_{n+1},\dots,\vec{m}_{n+m}\}$ is a set
of $m$ masters issuing nonreal-time constrained requests. In our
model, each $\vec{m}_{j}$ in $\mathcal{M}_{NRT}$ needs only one
parameter, the service cycle, to model the current request it
issues.
\end{description}

Here, a question may arise, since each node has a global ID. Why
don't we just map nodes' IDs within two hops into a group of
frequency numbers and assign those numbers to all nodes within two
hops?

\section{Simulator}
\label{sec:sim}

If the model checker requests successors of a state which are not
created yet, the state space uses the simulator to create the
successors on-the-fly. To create successor states the simulator
conducts the following steps.
% enumerate
\begin{enumerate}
\item Load state into microcontroller model.
\item Determine assignments needed for resolving nondeterminism.
\item For each assignment.
      \begin{enumerate}
      \item either call interrupt handler or simulate effect of next instruction, or
      \item evaluate truth values of atomic propositions.
      \end{enumerate}
\item Return resulting states.
\end{enumerate}
Figure~\ref{fig:one} shows a typical microcontroller C program that
controls an automotive power window lift. The program is one of the
programs used in the case study described in Section~\ref{sec:sim}.
At first sight, the programs looks like an ANSI~C program. It
contains function calls, assignments, if clauses, and while loops.
% Figure
\begin{figure}
\caption{Code before preprocessing.}
\label{fig:one}
\end{figure}

\subsection{Problem Formulation}

The objective of variable coalescence-based offset assignment is to find
both the coalescence scheme and the MWPC on the coalesced graph. We start
with a few definitions and lemmas for variable coalescence.

% Enunciations
\begin{definition}[Coalesced Node (C-Node)]A C-node is a set of
live ranges (webs) in the AG or IG that are coalesced. Nodes within the same
C-node cannot interfere with each other on the IG. Before any coalescing is
done, each live range is a C-node by itself.
\end{definition}

\begin{definition}[C-AG (Coalesced Access Graph)]The C-AG is the access
graph after node coalescence, which is composed of all C-nodes and C-edges.
\end{definition}

\begin{lemma}
The C-MWPC problem is NP-complete.
\end{lemma}
\begin{proof} C-MWPC can be easily reduced to the MWPC problem assuming a
coalescence graph without any edge or a fully connected interference graph.
Therefore, each C-node is an uncoalesced live range after value separation
and C-PC is equivalent to PC. A fully connected interference graph is made
possible when all live ranges interfere with each other. Thus, the C-MWPC
problem is NP-complete.
\end{proof}

\begin{lemma}[Lemma Subhead]The solution to the C-MWPC problem is no
worse than the solution to the MWPC.
\end{lemma}
\begin{proof}
Simply, any solution to the MWPC is also a solution to the
C-MWPC. But some solutions to C-MWPC may not apply to the MWPC (if any
coalescing were made).
\end{proof}

@@

% Start of "Sample References" section

\section{Typical references in new ACM Reference Format}
A paginated journal article \cite{Abril07}, an enumerated
journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96},
a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation \cite{Editor00}
followed by the same example, however we only output the series if the volume number is given
\cite{Editor00a} (so Editor00a's series should NOT be present since it has no vol. no.),
a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book
in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97},
an article in a proceedings (of a conference, symposium, workshop for example)
(paginated proceedings article) \cite{Andler79}, a proceedings article
with all possible elements \cite{Smith10}, an example of an enumerated
proceedings article \cite{VanGundy07},
an informally published work \cite{Harel78}, a doctoral dissertation \cite{Clarkson85},
a master's thesis: \cite{anisi03}, an online document / world wide web resource \cite{Thornburg01}, \cite{Ablamowicz07},
\cite{Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03}
and \cite{Lee05} and (Case 3) a patent \cite{JoeScientist001},
work accepted for publication \cite{rous08}, 'YYYYb'-test for prolific author
\cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might contain
'duplicate' DOI and URLs (some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}.
Boris / Barbara Beeton: multi-volume works as books
\cite{MR781536} and \cite{MR781537}.

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{acmsmall-sample-bibfile}
\bibliography{papers}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

>>>>

\section{Hardware}

Hardware underpins all of modern computing. While most software is
constructed and written in such a way as to abstract the
peculiarities of the underlying hardware, the software cannot
execute without hardware. In our abstracted model of the computing
stack, hardware is at the bottom, which means that it has complete
control of the computing system.

For hardware here, we consider all types of hardware in the computing
system: CPUs, SoCs, or any other integrated circuit (IC) that performs
computation or communication on behalf of the upper computing layers.
This also includes networking cards and other peripheral devices
(Bluetooth or USB devices), which may have their own special purpose
embedded hardware.

A key difficulty in analyzing the security concerns of hardware is
reverse engineering the workings of the hardware. Traditional
techniques to reverse engineer hardware require destroying the chip,
and if a single hardware component is destroyed to reverse engineer,
there is no guarantee that other hardware is identical to the reverse
engineered chip.

\subsection{Threats}

As the lower-most level of the computing stack, all layers implicitly
trust that the hardware is executing correctly. Therefore, if an
adversary is able to maliciously control the hardware execution, they
can compromise all layers of the computing stack. Thus, the security
of the hardware is of paramount importance.

The main threat considered by the literature on hardware is the threat
of Trojan logic. This is malicious logic that is introduced into the
% adversary, by definition is a malicious entity.
hardware chip by an adversary. Trojan introduction can be
done at several points of the hardware lifecycle:

\begin{itemize}

	\item \textbf{Design}. A malicious insider can incorporate a Trojan into the
	design of the hardware.

	\item \textbf{Third-party IP}. Oftentimes, hardware designers will take
	advantage of the functionality of third-party components, using them
	as a black-box. Thus, a third-party can include malicious Trojan
	logic.

	\item \textbf{Compilation of Design}. When the design of the hardware is
	compiled, but before it is sent for fabrication, the design could be
	changed to incorporate the Trojan logic. Note that this differs from
	Design-time, because the Trojan logic is not included in the design.
	Consider the case of malware on a hardware designer's machine, which
	changes the design when it is compiled.

	\item \textbf{Manufacture}. A malicious manufacturer can introduce Trojan logic into hardware after the design is received but before the hardware
	is fabricated.

	\item \textbf{Delivery}. A malicious hardware component containing Trojan logic can be swapped with a benign component after fabrication but before
	delivery and installation.

\end{itemize}

The malicious Trojan logic behavior comes in three different forms:
% TODO: Sai: is this three or two??

\begin{itemize}

	\item \textbf{Trigger-based}. The malicious behavior or logic is only expressed when certain conditions are met. Consider a Trojan logic in a CPU,
	which changes the executing code to Ring 0 (with the most
	privileges) when a specific sequence of instructions are issued. The
	trigger can be internal to the chip, such as in the CPU case, or
	could be external, for instance a certain radio frequency will
	trigger the malicious code.

	\item \textbf{Constant}. The malicious behavior or logic is continually
	executed and subtly changes the output of the hardware in a way that
	compromises security. Consider a Trojan logic of a Wi-Fi card, which
	leaks the Wi-Fi passphrase by embedding it in the operating
	parameters of the Wi-Fi radio.

\end{itemize}

These features of Trojan logic in hardware drive the research that
attempts to detect them.

\subsection{Research}

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,
agrawal2007, banga2008, banga2008a, jin2008, du2010, narasimhan2011,
narasimhan2012, cao2013, davoodi2013, dworak2013, forte2013,
liu2013, liu2014, bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008, jin2010,
sturton2011, liu2013, jin2014, zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

Of particular practical interest is a description of \emph{actual
Trojan logic} discovered in the ProASIC3 Flash FPGA military
chip~\cite{skorobogatov2012}. While in this case it was not proved
that the logic introduced to the chip was intentionally malicious,
nevertheless there existed functionality in the hardware that was
explicitly denied by the hardware designer.

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,
li2008, salmani2009, hicks2010, rosenfeld2011, waksman2011,
bhunia2013, davoodi2013, rajendran2013, rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

JTAG is a main avenue of reverse engineering hardware, so some work
has investigated the problem of securing JTAG access to
hardware~\cite{rosenfeld2010, ren2015}. The main idea is to allow only
authenticated users to have access to the JTAG functionality, however
this increases the cost and complexity of implemented JTAG.

Another approach is to change the design of the chip to support
runtime monitoring~\cite{waksman2010}. In this way, the hardware
is monitoring itself, 
rather than external analysis of
side-channels. However, this has all the same drawbacks of changing
the design of hardware, in addition to not being robust in the face of
a powerful attacker who is able to alter the design.

Recent approaches suggest to use machine-learning techniques to
identify the Trojan logic~\cite{haider2015}. Another approach attempts
to use a formal verification technique in order to prove that no
malicious logic was added to the hardware~\cite{guo2015}.

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,
tehranipoor2010, guin2014, guin2014a, guin2014b}.

Important problems include how to deal with counterfeit chips, better
non-destructive examination methods, continuous monitoring of the
integrity not just at boot time, and detection of backdoors and 
``undocumented features''.  Hardware design can also be done to
aid this process, e.g., having some part of the chip consume more power
to make it more identifiable for authentication purposes.  Other
possibilities include running multiple chips with different
implementations side-by-side and comparing results to detect unexpected
behavior.

\subsection{Suggested Focus Areas}

A key problem with hardware security is non-destructive IC
examination, identification, and authentication - how to ensure that
the chip that is designed is what is actually fabricated, with no
additional logic.

An additional neglected area is how to detect malicious Trojan logic
in third-party components. This would require some type of static
analysis or simulated dynamic analysis of third-party components,
which could detect Trojan logic.

Another approach that could be effective is how to properly test the
functionality of hardware after it has been fabricated. This could
include changing the design of the chip to allow better/more guided
fuzz testing of the chip itself, in order to discover the Trojan
logic.

Finally, a prevention approach could be taken, to monitoring the upper
layers of the computing stack for attempts to exploit the underlying
hardware. This can also include changing or altering the firmware
layer in such a way that it is not possible to exercise the Trojan
logic, potentially using randomization techniques similar to ASLR.

\section{Firmware}

%Note: I did not remove the previous versions of those paragraphs
%(commented them) so feel free to check the previous versions and 
%revert them if my changes have problems.

%Firmware is the layer of software that sits and interacts directly
%with the hardware. Typically, the firmware is controlled from the
%upper layers by device drivers in the Operating System.

%Faris:
Firmware is the layer of software that sits and interacts directly
with the hardware. Typically, the firmware is controlled by the
device drivers in the upper layers of the Operating System.

%Many different hardware contain firmware, for instance the boot BIOS
%on a motherboard is a form of firmware, embedded systems often contain
%specific firmware, hardware peripherals such as network cards contain
%firmware as well. We consider all such areas as firmware.

%Faris:
Many different hardware contain firmware. For instance: the boot BIOS
on a motherboard, embedded systems that contain
specific firmware, hardware peripherals such as network cards. 
We consider all such areas as firmware.

%The key traits of firmware is that, although it is binary code, it is
%operating/interacting directly with the hardware, so there are no
%%OS-style abstraction layers such as virtual memory, well-defined
%system calls, or hardware abstraction. Therefore, each firmware is
%binary code which is specifically tailored to a specific hardware
%platform.

%Faris:
Although firmware is binary code, it is
operating/interacting directly with the hardware, so there are no
OS-style abstraction layers such as virtual memory, well-defined
system calls, or hardware abstraction which is the key trait of firmware. 
Therefore, each firmware is specifically tailored to a specific hardware platform.

%Due to the hardware-specific nature of firmware, \emph{reverse
%	engineering} is critical to understanding the firmware. In addition,
%reverse engineering is particularly challenging because source code is
%frequently unavailable, and vendors' desire to protect their
%intellectual property makes them actively obfuscate their
%firmware. All this means that, extracting semantically useful
%information from firmware is a key first step to performing any
%security analysis of the firmware.

%Faris:
Due to the hardware-specific nature of firmware, \emph{reverse
	engineering} is critical to understand it. In addition,
reverse engineering is particularly challenging because the source code is
frequently unavailable, and vendors' desire to protect their
intellectual property makes them actively obfuscate their
firmware. This means, extracting semantically useful
information from firmware is the first and key step to perform any
security analysis of the firmware.

\subsection{Threats}

As the lowest-level of software code in the computing stack, threats
to firmware can compromise the security of the entire machine.
Firmware security is concerned with two main threats: (1)
vulnerabilities in the firmware code itself which allow an attacker to
execute arbitrary code with the capabilities of the firmware and (2)
firmware with intentional Trojan (backdoor) capabilities.

%Vulnerabilities in the firmware code allow an attacker to execute
%arbitrary code with the permissions of the firmware. The class of
%vulnerabilities are not unique to firmware, as they are the same class
%of vulnerabilities that infect traditional binary software (buffer
%overflows, logic flaws, etc.). However, firmware typically has full
%control over the entire computing system, therefore vulnerabilities in
%firmware are much more severe than those in the application layer. In
%addition, if an attacker is able to persist their exploit --- because the
%compromise occurs at such a low layer of the computing system --- the
%attacker can persist \emph{even after reinstalling the operating
%	system or application}.

%Faris:
Vulnerabilities in the firmware code allow an attacker to execute
arbitrary code with the permissions of the firmware. The class of
vulnerabilities are not unique to firmware, as they are the same class
of vulnerabilities that infect traditional binary software (buffer
overflows, logic flaws, etc.). However, firmware typically has full
control over the entire computing system, therefore vulnerabilities in
firmware are much more severe than those in the application layer. In
addition, the attacker may remain in the system because the
compromise occurs at such a low layer of the computing system so the
exploit persists \emph{even after reinstalling the operating
	system or application}.

%The attack surface for firmware varies depending on where it is used.
%In the most general case, the attacks can come from the upper layers,
%specifically the Operating System or Hypervisor layers, as these are
%the layers of the computing stack that can directly communicate with the
%firmware. However, other firmware can be attacked either directly
%through the Hardware layer itself, or through the data being
%transmitted through the firmware from the hardware. For instance, a
%network card firmware could be attacked through network traffic that
%the firmware processes.

%Faris:
The attack surface for firmware varies depending on where it is used.
In the general case, the attacks can come from the upper layers,
specifically the Operating System or Hypervisor layers, as these are
the layers of the computing stack that can directly communicate with the
firmware. However, other firmware can be attacked either directly
through the Hardware layer, or through the data being
transmitted through the firmware from the hardware. For instance, a
network card firmware could be attacked through network traffic that
the firmware processes.

Traditional vulnerability analysis is not effective on firmware, due
to the specificity of the firmware for the specific hardware and the
lack of a well-defined operating system abstraction for the firmware
code. In essence, each firmware is a custom binary with little in the
way of assumptions that vulnerability analysis can take advantage of.

%Trojan capabilities in the firmware itself can allow a system to be
%remotely controlled or accessed. This is similar to a vulnerability,
%in that an attacker is able to control the firmware, however the key
%difference lies in the fact that Trojan behavior will be intentionally
%obfuscated by an attacker, whereas a vulnerability is accidentally
%introduced by a benign developer. Therefore, Trojan behavior is 
%more difficult to detect, because there is an active adversary who is
%intentionally obfuscating the behavior.

%Faris:
Trojan capabilities in the firmware can allow a system to be
remotely controlled or accessed. This is similar to a vulnerability,
in that an attacker is able to control the firmware, however the key
difference lies in the fact that Trojan behavior can be intentionally
obfuscated by an attacker, whereas a vulnerability can accidentally
introduced by a benign developer. Therefore, Trojan behavior is 
difficult to detect.

%Vulnerabilities in the firmware and Trojan capabilities are related
%because both require \emph{understanding} the behavior and semantics
%of the firmware code. This is why reverse engineering is such a
%critical component of securing the threats against the firmware layer:
%in order to detect either vulnerabilities or Trojan functionality, an
%automated tool must first understand the semantics of the particular
%firmware/hardware combination.

%Faris:
Vulnerabilities in the firmware and Trojan capabilities are related
because both require \emph{understanding} the behavior and semantics
of the firmware code. This is why reverse engineering is such a
critical component of securing the firmware layer against the threats.
In order to detect vulnerabilities or trojan functionality, an
automated tool must understand the semantics of the particular
firmware/hardware combination.

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006, cui2010, duflot2011, basnight2013, cui2013,
	zaddach2013, zaddach2013a, maskiewicz2014, stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

Other approaches are about how to prevent the tampering of
firmware~\cite{adelstein2002, zhou2007, zhou2009}. These protect from
the threat of tampering or altering the firmware, however it does not
address vulnerable firmware.

Another approach includes runtime monitoring into the
firmware, so that compromises can be detected~\cite{cui2010a,
	cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

Recent work has looked into the problem of updating the design of the
firmware so that it has security features, such as memory handling and
avoiding information leakage~\cite{koeberl2014, kauer2007}. However,
forcing firmware developers to use such features is an open issue.

Very few work has looked into how to reverse engineer and understand the
firmware~\cite{zaddach2014}. This problem is of particular interest,
as understanding the semantics of the firmware and how it interacts
with hardware is a key challenge.

Recent work has looked into how to detect vulnerabilities in
firmware~\cite{davidson2013, costin2014, shoshitaishvili2015}. One of
these has an excellent website\footnote{\url{http://firmware.re}}
that contains the results of their reverse engineering and
vulnerability analysis~\cite{costin2014}.

\subsection{Suggested Focus Areas}
%Faris: Some fixes below.
Of all the layers, firmware has received the least attention from the
research community. Therefore, we believe that focus on this research
area will yield significant dividends.

The major challenge with preventing firmware vulnerabilities is how to decouple
firmware from the hardware, potentially using emulation of the
hardware, in order to aid the analysis of the firmware.

In a similar vein, there is need for automated reverse engineering tools,
including analysis of memory layouts, code modules, even answering the
simple question of what is code in a firmware binary and what is data.

Finally, even if we find vulnerabilities or Trojan logic in a
firmware, there is still the unanswered question of how to patch or
update the functionality of the firmware while still guaranteeing the
behavior of the firmware. This is particularly complicated due to the
real-time requirements of the firmware and the potentially concurrent
executions.

@@

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{papers}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012
